Longitudinal analysis 

### 2020-04-11 production/prod_analysis-cfa.rmd

```{r}
source(file = "production/prod_polychoric.R")
corr.test(cor01$rho)
sjt.corr(data = cor01$rho,triangle = "lower",digits = 2)
sjt.corr(data = dat01,triangle = "lower",digits = 2,var.labels = " ")

corr <- psych::polychoric(data,  na.rm = TRUE)

```

@@

>>>>

@@

## Correlations

```{r compare corr, echo=TRUE, out.width=c('33%', '33%', '33%'),fig.cap="Mode 01, 02 and 03",fig.show='hold'}
corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
corrplot(cor02$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
corrplot(cor03$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

## Measurement model

### 2020-04-11 production/prod_analysis-long_invariance.rmd

---
title: "Longitudinal analysis "
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---
# Longitudinal analysis

>>>>

---
title: "Longitudinal analysis "
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_analysis-long_invariance.Rmd",output_format = "html_document"); browseURL(url = "production/prod_analysis-long_invariance.html")
```

# Longitudinal analysis
